QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-1.0.tex
reword to reduce by one comma

However, this diversity also implies that QP means very different things to different researchers. This is illustrated by the fact that the class of problems that we simply refer to here as ``QP'' might more accurately be called Mixed-Integer Quadratically-Constrained Quadratic Programming (MIQCQP) in the most general case. It is, therefore, perhaps not surprising that, unlike for ``simpler'' problems classes like Mixed-Integer Linear Programming \cite{Koch2011},  there has been, to date, no single library devoted to all different kinds of instances of QP.\todo{AG: many commas in this sentence} While several specialized libraries devoted to particular cases of QP are available, each of them is either focused on a particular application (a specific problem that can be modeled as a QP), or on QPs with specific structural properties that make them suitable for solution by some given class of algorithmic approaches. To the best of our knowledge, collecting a set of QP instances that is at the same time not overwhelmingly onerous but sufficiently challenging for the many different interested communities has not been attempted. This work constitutes a first step in this direction.

>>>>

However, this diversity also implies that QP means very different things to different researchers. This is illustrated by the fact that the class of problems that we simply refer to here as ``QP'' might more accurately be called Mixed-Integer Quadratically-Constrained Quadratic Programming (MIQCQP) in the most general case. Therefore, it is perhaps not surprising that, unlike for ``simpler'' problems classes like Mixed-Integer Linear Programming \cite{Koch2011},  there has been, to date, no single library devoted to all different kinds of instances of QP.\todo{AG: many commas in this sentence SV: I removed one.}\ While several specialized libraries devoted to particular cases of QP are available, each of them is either focused on a particular application (a specific problem that can be modeled as a QP), or on QPs with specific structural properties that make them suitable for solution by some given class of algorithmic approaches. To the best of our knowledge, collecting a set of QP instances that is at the same time not overwhelmingly onerous but sufficiently challenging for the many different interested communities has not been attempted. This work constitutes a first step in this direction.
